### 2020-11-10 expose/main.tex
Add Whitepaper and resources

\title{Messaging Architecture for Integration of Customer Self Services \\ Version 0.2}
\author{Jonas Gann}
\date{28 September 2020}

@@

\section{Context}
As a result of the 2020 pandemic, customer self-service (CSS) technologies reached a new level of importance \cite{covid}.
Many shops were closed due to government measurements and customers had to use their web
presences. CSS is a useful method to handle support for an increasing number of online customers. It enables them to search 
for contract data, change profile information, track shipment and much more without the need of human to human interaction.
This reduces cost and increases customer performance.

@@

Of course, the integration also has to perform according to requirements of both the EA and the CSS business connector.

As an integration does not only interface with systems but also delivers information and instructions, additional requirements 
relating to reliability e.g. scalability, failure safety have to be considered.

@@

The bachelor thesis defines a messaging architecture for integration of a CSS connector 
into enterprise architectures. This simplifies and speeds up integration by providing a solution reusable in many 
different scenarios. A messaging approach enables deployment on different heterogeneous landscapes through 
loose coupling. Loose coupling allows integrated systems to not make assumptions about each other and use a 
send-and-forget approach, simplifying their integration.

Messaging systems can also reliably handle communication through e.g load balancing and store-and-forward mechanisms.

@@

\textbf{CSS scenarios} get compiled from multiple resources in order to describe, what CSS looks like in practice.
A scenario might e.g. be "New Address": User wants to change the address in his profile.

@@

\textbf{Business processes} relevant for the CSS scenarios get selected from EAPs. Relevance means, that the process 
is part of or related to the scenario.
This can e.g. be "Change Address": Login, Edit Profile, Change Address, Save Changes

\textbf{Architecture bricks and data objects} contained by EAPs of selected business processes are evaluated in respect to their necessity 
for the process. They make up the enterprise architecture. Requirements of the EA 
regarding the consumption of CSS get analyzed. One requirement could e.g. be, that access to 
the "New Address" CSS scenario is required via a web server architecture brick. Another requirement might be, 
that data has to arrive in the correct order.

\textbf{The business connector} is constructed - based on CSS scenarios - as a black box of requirements regarding 
the access to EA systems and data objects. The black box also contains interfaces, which provide functionalities for CSS 
scenarios. It is not be included, how the business 
connector processes received data, triggers instructions to the EA or implements a service.
The business connector could e.g. consist of the requirements: access to identities, access to identity validation, 
access to profile data and of the interface "changeIdentityProfileProperty"

\textbf{An integration architecture} gets defined, which utilizes the selected business processes, architecture 
bricks and data objects in order to integrate the business connector. Purpose of the integration is to enable 
the EA and business connector to access each others functionalities according to their requirements.
Requirements relating to the internal data and instruction delivery of the integration architecture 
like e.g. scalability and fail safety get considered in addition.
Architecture bricks and data objects used in the final form of the 
integration architecture can be seen as its requirements towards an existing EA.

\textbf{A messaging approach} based on enterprise integration patterns described
by \textcite{integrationPatterns} is used for the integration architecture.
It gets documented as a component diagram
containing architecture bricks, integration patterns and business connector along with communication 
channels and respective message layouts \cite[cf. 16 ff.]{integrationPatterns}.
For each CSS scenario, relevant data and instruction flows inside the integration architecture 
are visualized as a sequence diagram.

\textbf{Technologies} which can be used for implementation get evaluated for the final form of the integration architecture.
These can e.g. be different message oriented middlewares used for implementing messaging systems in general.

\textbf{An operation manual} with the purpose of guiding the requirement analysis in respect to existing architecture bricks and data 
objects of the EA and helping with theoretical and practical deployment of the integration architecture gets constructed.
It might e.g. help finding architecture bricks required by the integration architecture inside the EA 
and instruct on how to implement the integration architecture in practice.

\textbf{A validation} of results is done through a customer example. For given 
EA, business processes, business connector and customer specific requirements, the integration architecture gets 
deployed (in theory) by usage of the operation manual.
The quality of the integration architecture is measured by ease of deployment (e.g. used time) and 
satisfaction of requirements.

\section{Related Work}

\begin{itemize}
    \item "Enterprise Architecture Patterns" \cite{architecturePatterns}: This book presents how to construct and use so 
    called enterprise architecture patterns and documents 13 common examples. 
    \item "Enterprise Integration Patterns" \cite{integrationPatterns}: This book documents fundamental messaging patterns, 
    which can be used for integration purposes.
\end{itemize}

@@

The bachelor thesis is planned to be officially registered in November and finished in February.
Parallel to the execution of described approaches, relating chapters of the bachelor thesis will be written.

>>>>

\title{Messaging Architecture for Integration of Customer Self-Services}
\author{Jonas Gann}
\date{29 September 2020}

@@

\section{Context}
As a result of the 2020 COVID-19 pandemic, customer self-service (CSS) technologies reached a new level of importance.
Many shops were closed due to government measurements and customers had to use their web
presences. CSS is a useful method to handle support for an increasing number of online customers. It enables searching
for contract data, changing profile information, tracking shipment and much more without the need of human to human interaction.
This reduces cost and increases customer performance \cite{covid}.

@@

The integration also has to perform according to requirements of both the EA and the CSS business connector.

As an integration does not only interface with systems but also delivers information and instructions, additional requirements 
relating to reliability like scalability and failure safety have to be considered.

@@

The bachelor thesis defines a messaging architecture for integration of a business connector, providing an interface for CSS,  
into enterprise architectures. This simplifies and speeds up integration by providing a solution reusable in many 
different scenarios.

A messaging approach enables deployment on different heterogeneous landscapes through 
loose coupling. Loose coupling allows integrated systems to not make assumptions about each other and use a 
send-and-forget approach, simplifying their integration.

Mechanisms increasing reliability of message communication through for example load balancing and store-and-forward are part of the 
messaging approach.

@@

\textbf{CSS scenarios} get compiled from multiple resources in order to describe, what CSS looks like in practice.
A scenario might be "New Address: User wants to change the address in his profile".

@@

\textbf{Business processes} relevant for the CSS scenarios get selected from EAPs. A process is relevant if he
is part of or related to a scenario and can be "Change Address: Login, Edit Profile, Change Address, Save Changes"

\textbf{Architecture bricks and data objects} contained by EAPs of selected business processes are evaluated in respect to their necessity 
for the process. They make up the enterprise architecture. Requirements of the EA 
regarding the consumption of CSS get analyzed. One requirement could be, that access to 
the "New Address" CSS scenario is required via a web server architecture brick. Another requirement might be, 
that data has to arrive in the correct order.

The \textbf{business connector} is constructed - based on CSS scenarios - as a black box of requirements regarding 
the access to EA systems and data objects. The black box also contains interfaces which provide functionalities for CSS 
scenarios. It is not included, how the business 
connector processes received data, triggers instructions to the EA or implements a service.
The business connector could consist of the requirements: access to identities, access to identity validation, 
access to profile data and of the interface "changeIdentityProfileProperty"

An \textbf{integration architecture} gets defined which utilizes the selected business processes, architecture 
bricks and data objects in order to integrate the business connector. Purpose of the integration is to enable 
the EA and business connector to access each others functionalities according to their requirements.
Requirements relating to the internal data and instruction delivery of the integration architecture 
like scalability and fail safety get considered in addition.
Architecture bricks and data objects used in the final form of the 
integration architecture can be seen as its requirements towards an existing EA.

A \textbf{messaging approach} based on enterprise integration patterns described
by \textcite{integrationPatterns} is used for the integration architecture.
It gets documented as a component diagram
containing architecture bricks, integration patterns and business connector along with communication 
channels and respective message layouts \cite[cf. 16 ff.]{integrationPatterns}.
For each CSS scenario, relevant data and instruction flows inside the integration architecture 
are visualized as a sequence diagram.

\textbf{Technologies} which can be used for implementation get evaluated for the final form of the integration architecture.
These can be different message oriented middlewares used for implementing messaging systems in general.

An \textbf{operation manual} with the purpose of guiding the requirement analysis in respect to existing architecture bricks and data 
objects of the EA and helping with theoretical and practical deployment of the integration architecture gets constructed.
It might help finding architecture bricks required by the integration architecture inside the EA 
and instruct on how to implement the integration architecture in practice.

A \textbf{validation} of results is done through a real life example. For given 
EA, business processes, business connector and customer specific requirements, the integration architecture gets 
deployed (in theory) by usage of the operation manual.
The quality of the integration architecture is measured by ease of deployment (e.g. used time) and 
satisfaction of requirements.

@@

The bachelor thesis is planned to be officially registered at the beginning of November and finished at the end of February.
Parallel to the execution of described approaches, relating chapters of the bachelor thesis will be written.

### 2020-11-10 thesis/msc-thesis.tex
Add Whitepaper and resources

Digital customer self-service (DCSS) is a great tool for improving customer experience and reducing cost. Many enterprises therefore heavily
rely on it for main business services. Especially recent governmental regulations like "Onlinezugangsgesetz" (OZG), "Datenschutzgrundverordnung"
(DSGVO) and "Digitale Versorgung Gesetz" (DVG) have increased requirements for DCSS capabilities.

DCSS is made available through DCSS providers. They can consist of websites and applications developed in self-work or be 
services provided by separate companies.

Adding DCSS to a system architecture is a common task. It usually involves integration of new DCSS components
into an existing system architecture. Due to the complicated nature of system architectures, integration proves to be a difficult
task.

@@

Based on scenarios resulting from governmental regulations (due to their current relevance), an integration architecture is presented, which describes
their integration. It provides information on which type of systems and data objects an existing
architecture requires. It models how CSS providers and system architectures can communicate -
deliver data and instructions. And it shows how, with fast development and deployment speed, integration can be applied to
heterogeneous system architectures, be non-invasive and reliable.

@@

\chapter{Digital Customer Self-Service (DCSS)}

@@

\textbf{Example 1}: A service is the availability to purchase items whereas digital self-service is the order placement over a website.

@@

\section{DSGVO}

\section{DVG}

\chapter{DCSS Providers}

\todo[inline, caption={Write CSS Providers Chapter}]{Explain what CSS Providers are (what services they can provide -> what IDAS does) and how they can help creating DCSS.
     Also explain the concept of a business connector as technological communication point of the CSS provider}

\section{Description}

\section{CSS Solutions}

\chapter{DCSS Scenarios}

Usage of DCSS OZG scenarios (\textbf{process diagrams and data schemas available}
\cite{ozgScenarios}), DSGVO scenarios (textual description available \cite{dsgvo}) and DVG scenarios
(textual desciption available \cite{gematik-e-rezept})
\\\\
The scenarios include more than just CSS and are partly non-digital. Therefore processes relevant for DCSS have to be selected
and it has to be defined which processes are part of a CSS provider, the business systems or the integration architecture:

\subsection{Unemployment Benefit (AG2)}
\textbf{Available Resources}
\begin{itemize}
     \item Data Schema
     \item Process Diagram
     \item Process Diagram of Application
     \item Click-Dummy
\end{itemize}

\subsection{Training Promotion (BAföG)}
\textbf{Available Resources}
\begin{itemize}
     \item Data Schema
     \item Process Diagram
     \item Click-Dummy
\end{itemize}

\subsection{Drivers License}
\textbf{Available Resources}
\begin{itemize}
     \item Data Schema
     \item Process Diagram
     \item Process Diagram of Application
     \item Click-Dummy
\end{itemize}

\subsection{Company Registration and Approval}
\textbf{Available Resources}
\begin{itemize}
     \item Data Schema
     \item Process Diagram
     \item Click-Dummy
\end{itemize}

\subsection{Visa Issuance}
\textbf{Available Resources}
\begin{itemize}
     \item Data Schema
     \item Process Diagram
\end{itemize}

\section{DSGVO}

The DSGVO influences DCSS by regulating how digitally collected personal information (which is common in DCSS) has to be managed. This means, DCSS providers have to 
keep this regulation in mind when designing their solutions. It has implications on integration in that DSGVO compliance requires special management of data, 
which an integration system has to make possible (DCSS providers use it).

It has to be analyzed in regard to:
\begin{enumerate}
     \item Which parts of the regulation describe requirements for features of DCSS providers
     \item Which parts of the regulation describe requirements for integrations
\end{enumerate}

\subsection{Transparent Accessability}
The enterprise or organization can have the duty to make information about personal data accessible in transparent and understandable ways

\subsection{Deletion of Personal Data}
The user can have the right of removal of personal data

\subsection{Correction of Personal Data}
The user can have the right of modification of personal data.

\subsection{Information about collected Personal Data}
The user can have the right to be informed about various information of collected and stored personal data such as usage, duration of storage, ...

\subsection{Restriction of Processing}
The user can have the right to restrict the way in which personal data is processed

\subsection{Availability of Transferral of Personal Data}
The user can have the right to transfer personal data to himself or separate entities (company, organization).

\section{DVG}

\subsection{e-Prescription}
Reference can be found in the "rzteblatt" \cite{Ärzteblatt}.
\\\\
The user can have the right to manage his prescriptions via an App. Doctors give digital prescriptions to users app,
which can digitally be used in pharmacies also without physically being there.
\\\\
Regulation: "Gesetz fï¿½r mehr Sicherheit in der Arzneimittelversorgung (GSAV)"
\\\\
e-Prescription processes \cite{gematik-e-rezept}
\begin{enumerate}
     \item Doctor creates digital prescription if he has access to "Telematikinfrastruktur" and "Heilberufausweis"
     \item Prescription is saved on "Telematikinfrastruktur"
     \item Doctor displays a QR-Code (prescription-token)
     \item Patient can receive QR-Code in App (or get a printout)
     \item Patient can check availability of drug in pharmacies via the app
     \item Patient can "apply" the prescription to a pharmacy via the app
     \item prescription is now irrevocably bound to the pharmacy and gets reserved
     \item pharmacy can use prescription-token (in QR-Code) to access prescription in "Telematikinfrastruktur"
     \item pharmacy notifies patient if or when the drug is available
     \item drug can be picked up by patient or be delivered
     \item If user picks drug up, he can show QR-Code in app or on printout (he got from doctor)
     \item pharmacy can access "Telematikinfrastruktur" to validate prescription
     \item pharmacy gives drug if validated
\end{enumerate}
~\\
Enterprises are "allowed" to provide the IT-Structure behind the App, meaning the communication with a pharmacy and the receiving of prescription-tokens.
\\\\
What are services and what are self-services in this scenario:
\begin{itemize}
     \item Service: Access to prescription. Self-service: Digital management of prescriptions (prescription-tokens) inside app
     \item Service: Receiving drug for valid prescription. Self-service: Digital delivery of prescription (prescription-token)
           to pharmacy and digital instruction of delivery of drug
\end{itemize}

\section{PSD2}

The regulation is about how digital payment self-service providers have to function. This includes their communication / integration\cite{psd2Summary}.
\\\\
Full law at \cite{psd2}
\\\\
Regulation: "Payment Services Directive 2" (PSD2) (European law)
\\\\
What are services and what are self-services in this scenario:
\begin{itemize}
     \item Service: Payments and transfers. Self-service: Payment services are DCSS providers and offer digital execution of payments and transfers
\end{itemize}
~\\
The regulation has to be analyzed regarding:
\begin{enumerate}
     \item Which parts of the regulation describe required features of the self-service provider
     \item Which parts of the regulation describe requirements for integration
\end{enumerate}

\section{Requirements}

\chapter{Enterprise Architectures}

@@

\section{Modeling of the real world}

\section{Modeling Challenges}

\section{Enterprise Architecture Patterns (EAP)}

\chapter{Relevant Systems and Data}

\section{EAPs}

\section{Architecture Bricks}

\section{Data Bricks}

\section{Integration Requirements}

\subsection{Regarding Integration Architecture}

\subsection{Regarding Business Connector}

\chapter{Integration}

@@

>>>>

Many enterprises provide digital tools which improve service usability for their customers. For example: If somebody wants to watch a movie, he does 
not drive to the nearest store to buy a DVD but instead uses websites providing video on demand (VoD). The reason is: 
VoD enterprises provide tools for digital customer self-service (DCSS). A customer can easily access the video over a website on his own.
DCSS becomes increasingly relevant, as the german government introduced requirements for DCSS in many recent regulations. 
Most prominent are  "Onlinezugangsgesetz" (OZG), "Datenschutzgrundverordnung" (DSGVO) and "Digitale Versorgung Gesetz" (DVG).

DCSS is made available through DCSS providers. They can consist of websites and applications developed in self-work or be 
services provided by separate companies. Adding DCSS providers to a system architecture is a common task. It usually involves integration 
of new DCSS components into an existing system architecture. Due to the complicated nature of system architectures, integration proves to 
be a difficult task.

@@

Based on scenarios resulting from OZG, an integration architecture is presented, which describes
their integration. It provides information on which type of systems and data objects an existing
architecture requires. It models how CSS providers and system architectures can communicate -
deliver data and instructions. And it shows how, with fast development and deployment speed, integration can be applied to
heterogeneous system architectures, be non-invasive and reliable. The integration architecture enables expansion with 
self-service capabilities of different areas (e.g. online payment / shopping / information self-service) through future work.

@@

\chapter{Fundamentals}

\section{Digital Customer Self-Service}

@@

\textbf{Example 1}: A service is the availability to purchase items whereas digital self-service is the placement of orders over a website.

@@

\section{DCSS Provider}

\todo[inline, caption={Write DCSS Providers Chapter}]{Explain what DCSS Providers are (what services they can provide) and how they can help creating DCSS.
     Also explain the concept of a business connector as technological communication point of the DCSS provider}

\subsection{Description}

\subsection{CSS Solutions}

\subsection{Business Connector}

\section{Enterprise Architecture}

@@

\subsection{Modeling of the real world}

\subsection{Modeling Challenges}

\subsection{Enterprise Architecture Patterns (EAP)}

\section{Integration}

@@

\chapter{Outlook}

\begin{itemize}
     \item Expanding integration architecture with capabilities for DCSS scenarios of different areas than online administration self-service
     \begin{itemize}
          \item online payment self-service (PayPal, psd2)
          \item online shopping self-service (Amazon)
          \item online health care self-service (DVG)
          \item online entertainment self-service (Netflix, YouTube, Spotify)
          \item online information / support self-service (StackOverflow)
     \end{itemize}
\end{itemize}
